The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-09-01 ms/ms.tex
Updates from Overleaf

Land only caveat? Our PPE is run as land-only simulations, using prescribed atmospheric forcing. This is likely to be adequate for estimating many land surface fluxes and pools, in particular of carbon, but could lead to biased estimates of water and energy fluxes, as we know that atmospheric feedbacks to land surface characteristics modify the state of the land surface itself (Laguë et al. 2019). Additional work is planned to leverage this one-at-a-time land-only PPE to quatnify how much, where, and for which processes atmospheric feedbacks are likely to change the land surface state substatnially.

>>>>

Land only caveat? Our PPE is run as land-only simulations, using prescribed atmospheric forcing. This is likely to be adequate for estimating many land surface fluxes and pools, in particular of carbon, but could lead to biased estimates of water and energy fluxes, as we know that atmospheric feedbacks to land surface characteristics modify the state of the land surface itself (Laguë et al. 2019). Additional work is planned to leverage this one-at-a-time land-only PPE to quantify how much, where, and for which processes atmospheric feedbacks are likely to change the land surface state substantially.
